Many Analystis Project

### 2021-10-08 analysis.Rmd
Update analysis.Rmd

```{r}
# get data into shape
d1 <- df %>%
  dplyr::filter(
    !is.na(wb_psychANXIETY),
    !is.na(age),
    !is.na(rel_CHURCHFREQ),
   # !is.na(wb_psychMEANING),
    !is.na(male),
    !is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    anx_s = scale(wb_psychANXIETY),
    #put outcome in ST units (see McElreath 2021)  # not necessary
    age_s = scale(age),
    ch = rel_CHURCHFREQ,
    mn  = wb_psychMEANING,
    bg =  rel_EXTENTBELIEVEGOD,
    ch_s = scale(rel_CHURCHFREQ),
    mn_s = scale(wb_psychMEANING),
    bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx,
                ch,
                mn,
                bg,
                anx_s,
                age_s,
                ch_s,
                mn_s,
                male2,
                country,
                male,
                bg_s,
                wb_psychANXIETY)

@@

d0a <-ggdag::ggdag(dg1a, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("What if we were to assume distressing events increase belief in God?")
# graph adjustment sets

d1a<-ggdag::ggdag_adjustment_set(dg1a, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("If we assume distressing events increase Religious Belief, 
Religious Service as well as anxiety, crossectional data cannot avoid confounding ")

@@

dg1 <- dagify(
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church + U,
  church ~ age + male + country + U,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) #%>%#%>%
 # tidy_dagitty()       
# 
dp0 <-ggdag::ggdag(dg1, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("Assumed Causal Relations")

@@

```{r}
library("ggdag")
dg2 <- dagify(
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church + U,
  church ~ age + male + country,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "church",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) %>%
  tidy_dagitty()

@@

ggdag::ggdag(dg2, text = FALSE, use_labels = "label")  + theme_dag()
# graph adjustment sets
dp2<-ggdag::ggdag_adjustment_set(dg2, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for Religious Service
assuming service does not change from distress")

@@

dpz <- dagify(
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church,
  church ~ age + male + country,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) %>%
  tidy_dagitty()

ggdag::ggdag(dgz) + theme_dag()

# graph adjustment sets
dg1<-ggdag::ggdag_adjustment_set(dg1z, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for Religious Belief
assuming belief does not change from distress")

@@

```{r}
library(patchwork)
 (dp0 + d1a)/   (dg1 + dp2)  +   plot_layout(guides = 'collect')  + plot_annotation(title = 'If distressing life events affect religious belief and behaviour, longtidinal data are needed for causal inference', tag_levels = "a") 
# dag_ful 15/15
```

@@

parameters::model_parameters(m1, test = "p_direction")
brms::ranef(m1)
summary(m1)
```

@@

Believe in God predicts less anxiety

@@

```{r}
parR1<-parameters::model_parameters(m1,effects = "random" ) 
belief_random <- plot(parR1,  sort = TRUE) +theme_lucid()  + labs(title = "Country level heterogeneity in belief (co)-variances: India is an outlier.") 
```

@@

```{r, cache = TRUE}
library(viridis)
p0<-brms::conditional_effects(m1, "bg_s", 
                              spaghetti = T,
                              ndraws = 200,
                              categorical = T,
                              prob = .89,
                              method = 'fitted')

belief_fixed <- plot(p0, plot = FALSE)[[1]]   + xlab("belief (standardised)") + ylab ("anxiety (ordinal 1-5)") +
  labs(title = "Increasing belief predicts increasing anxiety")
```

@@

```{r echo}
glimpse(d1)
m2 <- brm(
    anx ~ ch_s +
    age_s  +
    male +
    (1 + ch_s | country),
  data = d1,
  family = cumulative(link ="logit"),
  seed = 1234,
  warmup = 1000,
  iter = 3000,
  chains = 4,
  file = here::here("models", "m1o_real")
)
```

@@

```{r}
parcR<-parameters::model_parameters(m2,effects = "random" ) 
church_random <- plot(parcR,  sort = TRUE) +theme_lucid() + labs(title = "Country level heterogeneity in religious service (co)-variances: India is again an outlier.") #option -->
```

@@

```{r, cache = TRUE}
library(viridis)
p0b<-brms::conditional_effects(m2, "ch_s", 
                              spaghetti = T,
                              ndraws = 200,
                              categorical = T,
                              prob = .89,
                              method = 'fitted')

church_fixed <-plot(p0b, plot = FALSE)[[1]]  + xlab("religious service attendance (standardised)") + ylab ("anxiety (ordinal 1-5)") +
  labs(title = "Increasing religious service attendence predicts lower anxiety.")

@@

Combined plot

```{r}
(belief_fixed + church_fixed )/( belief_random + church_random  ) +
  plot_annotation(tag_levels = "a") + plot_layout(guides = "collect")

# coef_graph 15 x 15 
```

@@

## Tables

### Anxiety ~ Belief

```{r}
library(kableExtra)
parameters::parameters(
  m1,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Belief in God is positively related to anxiety") %>%
    print()
```

### Anxiety ~ Chruch
```{r}
library(kableExtra)
parameters::parameters(
  m2,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Religious Service is negatively related to anxiety") %>%
    print()
```

@@

```{r}
set.seed(123)
n <- 1000
U <- rnorm( n ) # distressing events (unmeasured)
C <- rnorm( n, U ) # religious service attendance, increase with distress
B <- rnorm( n , C + U ) )# belief increase with service + distressing events
Y <- rnorm( n , U - C ) # measured distress caused by distress, reduced by church attendance.

@@

# summarise results
summary(
  mod1 <- lm(Anxiety ~ Belief + ReligiousService, data = simdat)
)
```

@@

```{r}
sim_fun = function() {
n <- 1000
U <- rnorm( n ) # distressing events (unmeasured)
C <- rnorm( n, U ) # religious service attendance, increase with distress
B <- rnorm( n , C + U ) # belief increase with service + distressing events
Y <- rnorm( n , U - C ) # measured distress caused by distress, reduced by church attendance. 
# simulate data
simdat <- data.frame(Belief = B, # belief
  ReligiousService = C, # religious service
  U = U, # distressing events (unmeasured)
  Anxiety = Y)
  sim_s <- lm(Anxiety ~ Belief + ReligiousService, data = simdat)
  sim_s
}

@@

# proportion of service coefficient p.values < .001
sum(tout$estimate > 0) / length(tout$estimate)
```

@@

>>>>

```{r}
# get data into shape
d1 <- df %>%
  dplyr::filter(
    !is.na(wb_psychANXIETY),
    !is.na(age),
    !is.na(rel_CHURCHFREQ),
   # !is.na(wb_psychMEANING),
    !is.na(male),
    !is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    anx_s = scale(anx),
    #put outcome in ST units (see McElreath 2021)  # not necessary
    age_s = scale(age),
    ch = rel_CHURCHFREQ,
    mn  = wb_psychMEANING,
    bg =  rel_EXTENTBELIEVEGOD,
    ch_s = scale(rel_CHURCHFREQ),
    mn_s = scale(wb_psychMEANING),
    bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx,
                ch,
                mn,
                bg,
                anx_s,
                age_s,
                ch_s,
                mn_s,
                male2,
                country,
                male,
                bg_s,
                wb_psychANXIETY)

@@

d0a <-ggdag::ggdag(dg1a, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("What if we were to assume distressing events increase belief in God?")
d0a
# graph adjustment sets

d1a<-ggdag::ggdag_adjustment_set(dg1a, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("If we assume distressing events affect belief and service we cannot estimate causal effects ")

@@

dg1 <- dagify(
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church + U,
  church ~ age + male + country + U,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) #%>%#%>%
 # tidy_dagitty()       
# 
dp0 <-ggdag::ggdag(dg1, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("Assumed unmeasured causal effects of distressing experiences")

@@

```{r}
library("ggdag")
dg2 <- dagify(
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church,
  church ~ age + male + country,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "church",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) %>%
  tidy_dagitty()

@@

nocause <- ggdag::ggdag(dg2, text = FALSE, use_labels = "label")  + theme_dag() + labs(title = "Assume unmeasured distressing experience
does not affect Belief or Service")
nocause

dp2<-ggdag::ggdag_adjustment_set(dg2, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for Religious Service
assuming service does not change from distress")

@@

dpz <- dagify(
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church,
  church ~ age + male + country,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
)

ggdag::ggdag(dpz) + theme_dag()

# graph adjustment sets
dg1<-ggdag::ggdag_adjustment_set(dpz, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for Religious Belief
assuming belief does not change from distress")

@@

## Anxiety causes belief DAG

```{r}
dpL <- dagify(
  anx  ~  church + male + country + U,
  belief ~ age + male + country + church + anx,
  church ~ age + male + country,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "anx",
  outcome =   "belief",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) %>%
  tidy_dagitty()

dl <- ggdag::ggdag(dpL, text = F, use_labels = "label") + theme_dag()
dl1<- dl + labs(title ="Assume Anxiety causes Belief in God")
dl1

dl2<-ggdag::ggdag_adjustment_set(dpL, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for Anxiety causing Belief in God")
dl2

## Anxiety causes church DAG

```{r}
dpC <- dagify(
  anx  ~   male + country + U,
  belief ~ age + male + country + church + anx,
  church ~ age + male + country,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "anx",
  outcome =   "church",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) %>%
  tidy_dagitty()

dC <- ggdag::ggdag(dpC, text = F, use_labels = "label") + theme_dag()
dlC<- dC + labs(title ="Assume Anxiety causes Religious Service")
dlC

dl2C<-ggdag::ggdag_adjustment_set(dpC, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for Anxiety causing Religious Service")
dl2C

## Dag graph

```{r}
library(patchwork)
 (dp0 + d1a)/   (nocause + dg1 + dp2)  /(dl1 + dl2 + dl2C)+   plot_layout(guides = 'collect')  + plot_annotation(title = 'Three causal models', tag_levels = "a") 
# dag_ful 20/20
```

@@

parameters::model_parameters(m1, test = "p_direction")
brms::ranef(m1)

parameters::parameters(
  m1,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Parameter estimates for model of Belief on Anxiety") %>%
    print()

@@

Believe in God predicts more anxiety

@@

```{r}
parR1<-parameters::model_parameters(m1,effects = "random" ) 
belief_random <- plot(parR1,  sort = TRUE) +theme_lucid()  + labs(title = "Country-level variability in anxiety intercepts are evident; country-level anxiety-on-belief co-variances
are not reliable: India is an outlier.") 
belief_random
```

@@

```{r, cache = TRUE}
library(viridis)
p0<-brms::conditional_effects(m1, "bg_s", 
                              spaghetti = T,
                              ndraws = 500,
                              categorical = T,
                              prob = .89,
                              method = 'fitted')

belief_fixed <- plot(p0, plot = FALSE)[[1]]   +  xlab("belief (standardised)") + ylab ("anxiety (ordinal 1-5)") + labs(title = "Increasing belief is associated with increasing anxiety")
belief_fixed
```

@@

```{r echo}
glimpse(d1)
m2 <- brm(
    anx ~ ch_s +
    age_s  +
    male +
    (1 + ch_s | country),
  data = d1,
  family = cumulative(link ="logit"),
  seed = 1234,
  warmup = 1000,
  iter = 3000,
  chains = 4,
  file = here::here("models", "m1o_real")
)

parameters::parameters(
  m2,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Parameter estimates for model of Religious Service on Anxiety") %>%
    print()
```

@@

```{r}
parcR<-parameters::model_parameters(m2,effects = "random" ) 
church_random <- plot(parcR,  sort = TRUE) +theme_lucid() + labs(title = "Country-level variability in anxiety intercepts are evident; country-level anxiety-on-service co-variances
are not reliable: India is again an outlier.")

church_random
```

@@

```{r, cache = TRUE}
library(viridis)
p0b<-brms::conditional_effects(m2, "ch_s", 
                              spaghetti = T,
                              ndraws = 500,
                              categorical =T,
                              prob = .89,
                              method = 'fitted')

church_fixed <-plot(p0b, plot = FALSE)[[1]]  + xlab("religious service attendance (standardised)") + ylab ("anxiety (ordinal 1-5)") +
  labs(title = "Increasing religious service attendence is associated with lower anxiety")

@@

## Results summary Belief ~ Anxiety

```{r}
m3<- brm(
  bg_s ~
    mo(anx)+
    ch_s +
    age_s  +
    male +
    (1 + mo(anx)| country),
  data = d1,
  seed = 1234,
  warmup = 1000,
  iter = 3000,
  chains = 4,
  file = here::here("models", "m3o_real")
)

parameters::model_parameters(m3, test = "p_direction")
brms::ranef(m3)

parameters::parameters(
  m3,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Parameter estimates for model of Anxiety on Belief") %>%
    print()
```

<!-- ```{r} -->
<!-- this is no better -->
<!-- m3a<- brm( -->
<!--   bg_s ~ -->
<!--     anx_s+ -->
<!--     ch_s + -->
<!--     age_s  + -->
<!--     male + -->
<!--     (1 + anx_s | country), -->
<!--   data = d1, -->
<!--   seed = 1234, -->
<!--   warmup = 1000, -->
<!--   iter = 3000, -->
<!--   chains = 4, -->
<!--   file = here::here("models", "m3a") -->
<!-- ) -->

<!-- parameters::model_parameters(m3a, test = "p_direction") -->
<!-- brms::ranef(m3a) -->
<!-- summary(m3a) -->
<!-- hist(d1$bg_s) -->
<!-- # YES -->
<!-- pp_check(m3a) -->
<!-- ``` -->

Anxiety predicts belief

```{r}
parF3 <- parameters::model_parameters(m3 ) 
parF3
plot(parF3,  sort = TRUE) +theme_lucid() #option -->
```

```{r}
parR3<-parameters::model_parameters(m3,effects = "random" ) 
anx_belief_random <- plot(parR3,  sort = TRUE) +theme_lucid()  + labs(title = "Country-level variabilty in belief intercepts are evident; country-level belief-on-anxiety co-variances
are not reliable.")

anx_belief_random
```

```{r}
plot(ggeffects::ggpredict(
  m3,
  terms = c("country[all]", "anx"),
  type = "re",
  ci.lvl = 0.89
)) + scale_color_viridis_d() +  scale_y_continuous(limits = c(0,1)) + 
  theme_bw()
```

```{r, cache = TRUE}
library(viridis)
p3<-brms::conditional_effects(m3, "anx", 
                              spaghetti = T,
                              ndraws = 500,
                              categorical = F,
                              prob = .89,
                              method = 'fitted')

belief_anxiety_random_fixed <- plot(p3, plot = FALSE)[[1]]   + xlab("Anxiety (monotonic ordinal 1-5)") + ylab ("Belief in God( standardised))") +
  labs(title = "Increasing anxiety is associated with increasing belief in God")

belief_anxiety_random_fixed
```

```{r}
# YES
pp_check(m3)
```

```{r, cache = TRUE}
mcmc_plot(m3,
          type = "trace")
```

## Results summary Church ~ Anxiety

```{r}
m4<- brm(
  ch_s ~
    mo(anx)+
    age_s  +
    male +
    (1 + mo(anx)| country),
  data = d1,
  seed = 1234,
  warmup = 1000,
  iter = 3000,
  chains = 4,
  file = here::here("models", "m4o_real")
)

parameters::model_parameters(m4, test = "p_direction")
brms::ranef(m4)

parameters::parameters(
  m4,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Parameter estimates for model of Anxiety on Religious Service") %>%
    print()
```

<!-- ```{r} -->
<!-- this is no better -->
<!-- m3a<- brm( -->
<!--   bg_s ~ -->
<!--     anx_s+ -->
<!--     ch_s + -->
<!--     age_s  + -->
<!--     male + -->
<!--     (1 + anx_s | country), -->
<!--   data = d1, -->
<!--   seed = 1234, -->
<!--   warmup = 1000, -->
<!--   iter = 3000, -->
<!--   chains = 4, -->
<!--   file = here::here("models", "m3a") -->
<!-- ) -->

<!-- parameters::model_parameters(m3a, test = "p_direction") -->
<!-- brms::ranef(m3a) -->
<!-- summary(m3a) -->
<!-- hist(d1$bg_s) -->
<!-- # YES -->
<!-- pp_check(m3a) -->
<!-- ``` -->

Anxiety predicts belief

```{r}
parF4 <- parameters::model_parameters(m4 ) 
parF4
plot(parF4,  sort = TRUE) +theme_lucid() #option -->
```

```{r}
par4<-parameters::model_parameters(m4,effects = "random" ) 
anx_church_random <- plot(par4,  sort = TRUE) + theme_lucid()  + labs(title = "Country-level variabilty in religious service intercepts are evident; country-level service-on-anxiety co-variances
are not reliable.")

anx_church_random
```

```{r}
plot(ggeffects::ggpredict(
  m4,
  terms = c("country[all]", "anx"),
  type = "re",
  ci.lvl = 0.89
)) + scale_color_viridis_d() +  scale_y_continuous(limits = c(0,1)) + 
  theme_bw()
```

```{r, cache = TRUE}
library(viridis)
p4<-brms::conditional_effects(m4, "anx", 
                              spaghetti = T,
                              ndraws = 500,
                              categorical = F,
                              prob = .89,
                              method = 'fitted')

church_anxiety_random_fixed <- plot(p4, plot = FALSE)[[1]]   + xlab("Anxiety (monotonic ordinal 1-5)") + ylab ("Religious Service(standardised))") +
  labs(title = "Increasing anxiety is associated with decreasing church attendance.")

church_anxiety_random_fixed
```

```{r}
# YES
pp_check(m4)
```

```{r, cache = TRUE}
mcmc_plot(m4,
          type = "trace")
```

## Combined plot

```{r}
library(patchwork)

(belief_fixed +  belief_random)/(church_fixed+ church_random  ) / 
(belief_anxiety_random_fixed + anx_belief_random) / (church_anxiety_random_fixed + anx_church_random) +
  plot_annotation(tag_levels = "a")# + plot_layout(guides = "collect")

# coef_graph 15 x 25
```

@@

@@

```{r}
set.seed(123)
n <- 1000
# distressing events (unmeasured)
U <- rnorm( n ) 
# religious service attendance increases with distress
C <- rnorm( n, U ) 
# anxiety caused by distress experience and
# buffered by religious service
Y <- rnorm( n , U - C )

# belief increases with service, anxiety,
# and experience
B <- rnorm( n , Y + C + U )

@@

# summarise results
summary(
  mod1 <- lm(Anxiety ~ Belief + ReligiousService, data = simdat)
)

# summarise results
summary(
  mod1b <- lm(Anxiety ~ ReligiousService, data = simdat)
)

summary(
  mod2 <- lm(Belief  ~ Anxiety + ReligiousService, data = simdat)
)

summary(
  mod3 <- lm(ReligiousService  ~ Anxiety, data = simdat)
)

belief_on_anxiety_sim <- plot( ggeffects::ggpredict(mod1, terms = c("Belief")), add.data = TRUE, dot.alpha =.5 ) + labs(title = "Simulation recovers positive relationship between belief on anxiety") + scale_y_continuous(limits = c(-7,7))+ scale_x_continuous(limits = c(-10,10))

service_on_anxiety_sim <- plot( ggeffects::ggpredict(mod1b, terms = c("ReligiousService")), add.data = TRUE, dot.alpha =.5 ) + labs(title = "Simulation recovers negative relationship between religious service on anxiety")+ scale_y_continuous(limits = c(-7,7))+ scale_y_continuous(limits = c(-7,7))+ scale_x_continuous(limits = c(-10,10))
service_on_anxiety_sim

service_on_anxiety_sim <- plot( ggeffects::ggpredict(mod1, terms = c("ReligiousService")), add.data = TRUE, dot.alpha =.5 ) + labs(title = "Simulation recovers negative relationship between religious service on anxiety")+ scale_y_continuous(limits = c(-7,7))+ scale_x_continuous(limits = c(-10,10))
service_on_anxiety_sim

anxiety_on_belief_sim <- plot( ggeffects::ggpredict(mod2, terms = c("Anxiety")), add.data = TRUE, dot.alpha =.5 ) + labs(title = "Simulation recovers positive relationship between anxiety on belief")+ scale_y_continuous(limits = c(-7,7))+ scale_x_continuous(limits = c(-10,10))
anxiety_on_belief_sim

anxiety_on_church_sim <- plot( ggeffects::ggpredict(mod3, terms = c("Anxiety")), add.data = TRUE, dot.alpha =.5 ) + labs(title = "Simulation recovers negative relationship between anxiety on religious service")+ scale_y_continuous(limits = c(-7,7))
anxiety_on_church_sim

library(patchwork)

(belief_on_anxiety_sim +  service_on_anxiety_sim)/ (anxiety_on_belief_sim + anxiety_on_church_sim)

# sim_graph 15 x 15

@@

```{r}
sim_fun = function() {
n <- 1000
U <- rnorm( n ) # distressing events (unmeasured)
C <- rnorm( n, U ) # religious service attendance, increase with distress
Y <- rnorm( n , U - C ) # measured distress caused by distress, reduced by church attendance. 
B <- rnorm( n , Y + C + U )# belief increase with service + distressing events + anxiety

  sim_s <- lm(Anxiety ~ Belief + ReligiousService, data = simdat)
  sim_s
}

@@

# proportion of service coefficient p.values < .001
sum(tout$p.value <.001) / length(tout$p.value)
```

## Simulation tables

@@

parameters::parameters(
  mod2,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Same simulation tracks anxiety as cause of religious belief") %>%
    print()

parameters::parameters(
  mod3,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Same simulation tracks anxiety as cause of decling religious service") %>%
    print()
```
